### 2024-09-17 Response/Response.tex

%presents a more challenging problem. The impact of processing deadlines on the dynamic workload at the ENs influences the delay experienced by the offloaded tasks.

%In \cite{mao2016dynamic,zhang2016energy,bi2018computation,ning2018cooperative}, the processing capacity assigned to each MD by an EN remained unaffected by the number of offloaded tasks, resulting in a heavy load on the EN when a significant number of MDs offload their tasks to it. This heavy load can cause significant processing delays and even lead to missed deadlines and dropped tasks. To mitigate this issue, some existing works have proposed task offloading algorithms that consider the workloads at the ENs. In \cite{chen2018task}, Chen \textit{et al.} proposed an algorithm for task offloading in a software-defined ultra-dense network. The goal of this algorithm is to minimize task delay by formulating the task offloading scheme as a mixed integer non-linear program problem. Shah-Mansouri \textit{et al.} in \cite{shah2018hierarchical} proposed a QoE maximization slotwork for offloading decisions based on computation energy and delay reduction. They formulated a potential game to model competition among IoT users and achieved a close-to-optimal social cost.

\subsection{Related Work}
%\textcolor{black}{We explore state-of-the-art techniques characteristic to discuss how they address task offloading problems in scenarios that need to process massive data with limited devices in MEC, such as the Internet of Things (IoT), Internet of Vehicles (IoV), and Industrial IoT (IIoT)  environment.

	%Internet of Things (IoT) \cite{dai2020edge}, \cite{liao2023online}, \cite{Bolourian-WCL24}, 
	%Internet of Vehicles (IoV) \cite{Bolourian-WCL24}, 
	%and Industrial IoT (IIoT)  environment \cite{gong2022edge}, \cite{wu2023multi}, \cite{wu2024combining}

	%\subsubsection{DRL-Based Task Offloading Optimization in MEC}

	\textcolor{blue}{
		In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment. To take advantage of RL methods for online computation offloading in MEC, Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC. They proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL (MADRL), which can generate interactive information along with resource decisions. Zhou \textit{et al.} in \cite{zhou2021deep} used an MDP to model the interactions of the environment. They proposed a Q-learning approach to achieve optimal resource allocation strategies and computation offloading. Liao \textit{et al.} in \cite{liao2023online} introduced a double DRL algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption. }

	\textcolor{blue}{
		In these researches authors investigated simple MEC networks and explored computation offloading problems, mainly focused on delay-tolerant tasks or single MEC network model, and did not take into account the challenges of dynamic network environment with the variety of MDs and servers involved. In actual scenarios, an MEC system can provide delay-constrained services for serval MDs and ENs at the same time, while the works \cite{huang2019deep}, \cite{liu2021learn} not consider delay-sensitive tasks for network model and \cite{zhou2021deep}, \cite{liao2023online} just considered the situation of a single server or user in the MEC system.}

	\textcolor{blue}{  
		In fact, the state of MD's computing and transmission power, arrived task's requirement, the energy state of MDs, and workloads at ENs all change dynamically with time in actual systems, thus a more realistic MEC scenario is needed. Besides the works \cite{huang2019deep}--\cite{liao2023online}, Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a MARL method to minimize both energy consumption and processing delay. Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm to concurrently optimize resource allocation and computation offloading. To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent DDQN-based algorithm.
		In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility. In this approach, each MD requires quality-of-service information from other MDs.}

	%In these researchs authours mostly investigated MEC networks and explored computation offloading problem, but in some works such as \cite{zhou2021deep} \cite{liao2023online} have mainly focused on single MEC network model, and has not taken into account the challenges of dynamic network environment with multiple ENs. In fact, the channel quality, requested task, and energy state on an MDs all change dynamically with time in an actual MEC scenario, thus a more realistic MEC scenario is needed, involving delay-sensitive tasks with processing deadlines in multiple MDs and ENs, which poses a more intricate challenge.

	\textcolor{blue}{
		While studies like \cite{wu2023computation}--\cite{zhao2019deep} explored task offloading problems in a more advanced scenario and proposed some DRL-based algorithms, MEC systems often encounter challenges related to managing time-varying resource requests from heterogeneous devices, imposing significant challenges in resource accessibility and overall system performance. To address this issue, the authors applied queuing theory to model MEC systems more accurately, reflecting real-world scenarios. 
		%\subsubsection{Queuing Theory for Computation Offloading}
		In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered IoT devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation. Tang \textit{et al.} in \cite{9253665} investigated the task offloading problem for indivisible and deadline-constrained computational tasks in MEC systems. The authors proposed a distributed DRL-based offloading algorithm designed to handle uncertain workload dynamics at the ENs. 
		In \cite{huang2021deadline}, Huang \textit{et al.} proposed a DRL-based method based on a partially observable MDP (POMDP), which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks. To optimize delay and energy consumption in an MEC-based IIoT system, Wu \textit{et al.} in \cite{wu2023multi} proposed a multi-agent DQN-based method based on POMDP to address computation offloading problem. In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading.}

%	\begin{table*}[htbp]\textcolor{blue}{
%		\renewcommand{\arraystretch}{0.6}
%		\captionsetup{name=TABLE}
%		\caption{Comparison of Related Works Characteristic\vspace{4mm}}
%		\scalebox{0.7}{%
%			\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3cm}p{4.6cm}l} 
%				\toprule
%				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
%				\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a singel MEC system model  \\\midrule
%				\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule				
%				\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
%				\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent DDPG & Not take user's deman into consideration \\\midrule
%				\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
%				\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
%				\cite{wu2023computation} & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & MARL & Not consider tasks with maximum delay tolerance\\\midrule
%				\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's deman into consideration \\\midrule
%				\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & MADRL &  Not consider delay-sensitive tasks \\\midrule
%				\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's deman into consideration\\\midrule
%				\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent DDPG & Not take user's deman into consideration \\\midrule
%				\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
%				\cite{wu2024combining} & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & DDPG  & Not take user's deman into consideration \\\midrule
%				\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent DQN&  Not consider tasks with maximum delay tolerance \\\midrule
%				\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
%				\cite{Bolourian-WCL24} & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
%				QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
%				\toprule
%		\end{tabular}}
%		\label{table1}}
%\end{table*}

	\subsection{Motivation and Contributions}

	Although DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention.  \textcolor{blue}{As shown in Table~\ref{table1}, current research primarily focuses on minimizing energy consumption \cite{tang2022uav}, reducing processing delays \cite{guo2022energy}, \cite{seo2022differential}, maximizing computation rates~\cite{huang2019deep}, or optimizing a weighted balance among performance factors \cite{li2022joint}. However, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay, as considered in \cite{sun2024hierarchical}, \cite{9253665} but also by energy consumption \cite{Bolourian-WCL24}, \cite{huang2021deadline}. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs. 
		While some existing works such as \cite{liao2023online}, \cite{wu2024privacy}, \cite{dai2020edge}, \cite{gao2022large}, \cite{li2022joint} have investigated the trade-off between delay and energy consumption, they fail to address the user demands and fulfill QoE requirements properly.} In contrast to the aforementioned works, we propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their demands. %We also explore a more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, posing a more intricate challenge.

@@

%In the following, we first show the convergence of the proposed algorithm across episodes. Then, we compare the performance of our proposed algorithm with the benchmark methods under different parameter settings.

%In the following, we will compare the performance of the QECO algorithm with benchmark methods under two different computation workloads. This comparison will involve increasing the task arrival rate and the number of MDs.

%\newpage

%\begin{table}
%	\centering
%	\renewcommand{\arraystretch}{1}
%	\captionsetup{name=TABLE}
%	\caption{Simulation Parameters}
%	\scalebox{1}{%
%		\begin{tabular}{ l|l } 
%			%\toprule
%			\textbf{Parameter} & \textbf{Value}  \\ \hline
%			%\midrule
%			%Number of MDs $i$  & 50  \\ 
%			%Number of EN $j$  & 5  \\ 
%			%Number of episodes $N^{\text{ep}}$  & 1000  \\ 
%			%Number of time slots $T$  & 100 (with $\tau = 0.1$ second) \\ 
%			Computation capacity of MD $f_i$  & 2.6 GHz \\ 
%			Computation capacity of EN $f_j^{\text{E}}$ & 42.8 GHz  \\ 
%			Transmission capacity of MD $r_{i,j}(t)$ & 14 Mbps  \\ 
%			Task arrival rate & 150 Task/sec  \\ 
%			Size of task $\lambda_i(t)$  & $\{\text{1.0, 1.1, \ldots , 7.0}\}$ Mbits \\ 
%			Required CPU cycles of task $\rho_i(t)$  & $\{\text{0.197,0.297,0.397}\}$ $\times10^3$ \\ 
%			Deadline of task $ \Delta_i$  & 10 time slots (1 Sec)\\ 
%			Battery level percentage of MD $\phi_i(t)$  & $\{\text{25, 50, 75}\}$\\ %Percent \\ 
%			%Computation power of MD $p_i^{\text{C}}$ & \text{$10^{-27}(f_i)^3$}  \\ 
%			Computation power of EN $p_j^{\text{E}}$ & 5 W  \\ 
%			Transmission power of MD $p_i^{\text{T}}$ & 2.3 W  \\ 
%			Standby power of MD $p_i^{\text{I}}$& 0.1 W  \vspace{1mm}\\ 
%			%\toprule
%	\end{tabular}}
%	\label{table}
%\end{table}

@@

Figs.~\ref{chart2} (a) and ~\ref{chart2} (b) illustrate the overall energy consumption for different values of task arrival rate and the number of MDs, respectively. At the lower task arrival rate, the total energy consumption of all methods is close to each other. The total energy consumption increases when we have a higher task arrival rate.  
%When the task arrival rate increases, the total energy consumption of each method increases differently. It can be found that the production of more computational tasks leads to a continuous increase in energy consumption until the capacity is saturated, and the energy consumption remains constant at its maximum. The QECO algorithm takes into account the battery level of the MD in its decision-making process. 
As can be observed from Fig.~\ref{chart2} (a), at task arrival rate 450, QECO effectively reduces overall energy consumption by 18\% and 15\% compared to RD and PGOA, respectively, as it takes into account the battery level of the MD in its decision-making process. However, it consumes more energy compared to LC and FO because they do not utilize all computing resources. In particular, LC only uses the MD's computational resources, while FO utilizes the allocated EN computing resources.

\begin{figure}[tbp]
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.34\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ completed_tasks_1} 
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.34\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ completed_tasks_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	%\vspace{-0.65cm}
	\caption{The number of completed tasks under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart1}
\end{figure}

\begin{figure}[tbp]
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ energy_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	%\hspace{-0.2cm}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ energy_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	%\vspace{-0.7cm}
	\caption{The overall energy consumption under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart2}
\end{figure}

\begin{figure}[t]
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ delay_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ delay_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	%\vspace{-0.7cm}
	\caption{The average delay under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart3}
\end{figure}

\begin{figure}[tbp]
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.340\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ qoe_1} 		
		\textcolor{white}{i}\hspace{0.6cm}(a)
	\end{minipage}
	\hspace{-0.2cm}
	\begin{minipage}[b]{0.340\linewidth}
		\includegraphics[width=\textwidth]{ qoe_2}
		\textcolor{white}{i}\hspace{0.6cm}(b)
	\end{minipage}
	%\vspace{-0.7cm}
	\caption{The average QoE under different computation workloads: (a) task arrival rate; (b) the number of MDs.}
	\label{chart4}
\end{figure}

### 2024-09-17 Response/Response.tex

We finally delve into the investigation of the convergence performance of the QECO algorithm, which is shown through the average QoE across episodes in Figs.~\ref{chart0} (a) and~\ref{chart0} (b). We explore the impact of two main hyper-parameters on the convergence speed and the converged result of the proposed algorithm. Fig. \ref{chart0} (a) illustrates the convergence of the proposed algorithm under different learning rates, where the learning rate regulates the step size per iteration towards minimizing the loss function. The QECO algorithm achieves an average QoE of 0.77 after around 400 episodes when the learning rate is 0.001, indicating relatively rapid convergence. However, with smaller learning rates (e.g., 0.0001) or larger values (e.g., 0.01),  a slower convergence is observed. Fig. \ref{chart0} (b) shows the convergence of the proposed algorithm under different batch sizes, which refer to the number of sampled experiences in each training round. An improvement in convergence performance is observed as the batch size increases from 4 to 16. However, further increasing the batch size from 16 to 32 does not notably enhance the converged QoE or convergence speed. Hence, a batch size of 16 may be more appropriate for training processes.

\begin{figure}
	\centering
	\captionsetup{name=Fig.}
	\begin{minipage}[b]{0.34\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ conv1_f} 
		\textcolor{white}{i}\hspace{0.4cm}(a)
	\end{minipage}
	\hspace{-0.26cm}
	\begin{minipage}[b]{0.34\linewidth}
		\centering
		\includegraphics[width=\textwidth]{ conv2_f}
		\textcolor{white}{i}\hspace{0.4cm}(b)
	\end{minipage}

	\caption{The convergence of the average QoE across episodes under different hyper-parameters: (a) Learning rate; (b) Batch size.}
	\label{chart0}
\end{figure}

@@

\setcounter{section}{0}
\renewcommand*{\thesection}{\Roman{section}}
\makeatletter

\newpage

\section{Response to Reviewer 1}
\begin{enumerate}

\item \underline{Reviewer's Comment}: 
\textit{``(a) Lots of the studies focus on the research on resource optimisation of MEC by DRL, it is expected to survey the state-of-the-art within 3 years, and summarise it as an individual section, departing from the Section of Introduction. (b) Besides, the existing related work only has one paragraph without any discussion about the pros/cons of the previous work.''} \newline

\underline{Authors' Reply}: (a) To address the reviewer comment about state-of-the-art within 3 years discusion, we have added this paragraph to the Section I, as follows. \newline
	\begin{my}{1cm}{1cm}
	\rev{\,\,\,\, To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) hold promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives \cite{arulkumaran2017deep}. RL can effectively tackle the challenges of MEC arising from the ever-changing nature of networks, MDs, and servers' heterogeneity. This ultimately improves the MD users' QoE. We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL (MARL) framework for self-powered MEC. Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the industrial IoT (IIoT) systems to jointly optimize task offloading and resource allocation to achieve lower energy consumption and decreased task delay. To investigate privacy aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} proposed a deep Q-network (DQN)-based method. They transform the problem on MDP to optimize computation rate and energy consumption in a queuing-based IIoT network. Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.}
\end{my}

\vspace{6mm}

(b) We have also revised the ralated works section, as below.\\

	\begin{my}{1cm}{1cm}
	\rev{\,\,\,\, In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment. To take advantage of RL methods for online computation offloading in MEC, Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC. They proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL (MADRL), which can generate interactive information along with resource decisions. Zhou \textit{et al.} in \cite{zhou2021deep} used an MDP to model the interactions of the environment. They proposed a Q-learning approach to achieve optimal resource allocation strategies and computation offloading. Liao \textit{et al.} in \cite{liao2023online} introduced a double DRL algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption.

	\,\,\,\, In these researches authors investigated simple MEC networks and explored computation offloading problems, mainly focused on delay-tolerant tasks or single MEC network model, and did not take into account the challenges of dynamic network environment with the variety of MDs and servers involved. In actual scenarios, an MEC system can provide delay-constrained services for serval MDs and ENs at the same time, while the works \cite{huang2019deep}, \cite{liu2021learn} not consider delay-sensitive tasks for network model and \cite{zhou2021deep}, \cite{liao2023online} just considered the situation of a single server or user in the MEC system.

\,\,\,\, In these researches authors investigated simple MEC networks and explored computation offloading problems, mainly focused on delay-tolerant tasks or single MEC network model, and did not take into account the challenges of dynamic network environment with the variety of MDs and servers involved. In actual scenarios, an MEC system can provide delay-constrained services for serval MDs and ENs at the same time, while the works \cite{huang2019deep}, \cite{liu2021learn} not consider delay-sensitive tasks for network model and \cite{zhou2021deep}, \cite{liao2023online} just considered the situation of a single server or user in the MEC system.

\,\,\,\, In fact, the state of MD's computing and transmission power, arrived task's requirement, the energy state of MDs, and workloads at ENs all change dynamically with time in actual systems, thus a more realistic MEC scenario is needed. Besides the works \cite{huang2019deep}--\cite{liao2023online}, Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a MARL method to minimize both energy consumption and processing delay. Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm to concurrently optimize resource allocation and computation offloading. To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent DDQN-based algorithm.
In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility. In this approach, each MD requires quality-of-service information from other MDs.

\,\,\,\, While studies like \cite{wu2023computation}--\cite{zhao2019deep} explored task offloading problems in a more advanced scenario and proposed some DRL-based algorithms, MEC systems often encounter challenges related to managing time-varying resource requests from heterogeneous devices, imposing significant challenges in resource accessibility and overall system performance. To address this issue, the authors applied queuing theory to model MEC systems more accurately, reflecting real-world scenarios. 
In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered IoT devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation. Tang \textit{et al.} in \cite{9253665} investigated the task offloading problem for indivisible and deadline-constrained computational tasks in MEC systems. The authors proposed a distributed DRL-based offloading algorithm designed to handle uncertain workload dynamics at the ENs. 
In \cite{huang2021deadline}, Huang \textit{et al.} proposed a DRL-based method based on a partially observable MDP (POMDP), which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks. To optimize delay and energy consumption in an MEC-based IIoT system, Wu \textit{et al.} in \cite{wu2023multi} proposed a multi-agent DQN-based method based on POMDP to address computation offloading problem. In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading.}
\end{my}

\vspace{6mm}

We have also revised the motivation and contributions subsection, as below.

\vspace{6mm}

	\begin{my}{1cm}{1cm}
	\rev{\,\,\,\, Although DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention.  \textcolor{blue}{As shown in Table~\ref{table1}, current research primarily focuses on minimizing energy consumption \cite{tang2022uav}, reducing processing delays \cite{guo2022energy}, \cite{seo2022differential}, maximizing computation rates~\cite{huang2019deep}, or optimizing a weighted balance among performance factors \cite{li2022joint}. However, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay, as considered in \cite{sun2024hierarchical}, \cite{9253665} but also by energy consumption \cite{Bolourian-WCL24}, \cite{huang2021deadline}. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs. 
    While some existing works such as \cite{liao2023online}, \cite{wu2024privacy}, \cite{dai2020edge}, \cite{gao2022large}, \cite{li2022joint} have investigated the trade-off between delay and energy consumption, they fail to address the user demands and fulfill QoE requirements properly.} In contrast to the aforementioned works, we propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their demands.}
\end{my}

@@

\underline{Authors' Reply}:\\

\item \underline{Reviewer's Comment}: 
\textit{``Some sota methods (e.g., DDQN, DDPG) are expected to be compared in the section on performance evaluation, and authors should have more discussions about the evaluation results rather than merely introducing them. Besides, I think it is better to design the evaluations with a real dataset. Besides, 9\% and 6\% are not significant improvements compared to other methods.''} \newline

\underline{Authors' Reply}:\\

\item \underline{Reviewer's Comment}: 
\textit{``Other concerns are also expected to be addressed: (a) be careful to use words like "battery level" to express the energy consumption, because some of the energy is provided by the wired line power. (b) Most of the references are out of 3 years, please investigate more studies published in recent years.} (c) The authors should thoroughly check the writing style, grammar, and spelling to enhance the paper's clarity, conciseness, and overall impact.''\newline

\underline{Authors' Reply}: (a) We have changed the word "battry level" to "energy state" in whole paper of the revised manuscript. \newline

(b) We have added some related refrences, which are under 3 years, in Section I, as follow: \newline

		\begin{my}{1cm}{1cm}
	\rev{
		{\small
			\noindent\hspace{-0.3mm}\cite{munir2021multi} Munir, Md Shirajum and Tran, Nguyen H and Saad, Walid and Hong, Choong Seon, ``Multi-agent meta-reinforcement learning for self-powered and sustainable edge computing systems,'' \textit{IEEE Trans. Netw. Serv. Manag.}, vol. 18, no. 3, pp. 3353-3374. 2021.\\[6pt]
			\cite{wu2024combining} G. Wu, X. Chen, Y. Shen, Z. Xu, H. Zhang, S. Shen, and S. Yu,``Combining Lyapunov optimization with Actor-Critic networks for privacy-aware IIoT computation offloading,'' in \textit{IEEE Internet Things J.}, 2024, Early Access\\[6pt]
			\cite{lin2022multi} Lin, Shih-Yang and Huang, Chung-Ming and Wu, Tzu-Yu, ``Multi-access edge computing-based vehicle-vehicle-RSU data offloading over the multi-RSU-overlapped environment,'' \textit{IEEE Open J. Intell. Transp. Syst.}, vol. 3, pp. 7--32, 2022.\\[6pt]
			\cite{wei2023many} Wei, Zhiwei and Li, Bing and Zhang, Rongqing and Cheng, Xiang and Yang, Liuqing, ``Many-to-many task offloading in vehicular fog computing: A multi-agent deep reinforcement learning approach,'' \textit{IEEE Trans. Mob. Comput.}, vol. 23, no. 3, pp. 2107--2122, 2023.\\[6pt]
			\cite{wu2023multi} G. Wu, Z. Xu, H. Zhang, S. Shen, and S. Yu,  ``Multi-agent DRL for joint completion delay and energy consumption with queuing theory in MEC-based IIoT,'' in \textit{Journal of Parallel and Distributed Computing}, vol. 176, pp. 80–94, Jun. 2023.\\[6pt]
			\cite{wu2023computation} G. Wu, H. Wang, H. Zhang, Y. Zhao, S. Yu, and S. Shen, ``Computation offloading method using stochastic games for software-defined-network-based multiagent mobile edge computing,'' \textit{IEEE Internet Things J.}, vol. 10, no. 20, pp. 17620–17634, Oct. 2023.\\[6pt]
			\cite{wu2024privacy} G. Wu, X. Chen, Z. Gao, H. Zhang, S. Yu, and S. Shen, ``Privacy-preserving offloading scheme in multi-access mobile edge computing based on MADRL,'' \textit{Journal of Parallel and Distributed Computing}, vol. 10, no. 1, pp. 451--460, Mar. 2022.\\[6pt]
			\cite{yuan2023adaptive} Yuan, Shijing and Dong, Beiyu and Lvy, Hongtao and Liu, Hongze and Chen, Hongyang and Wu, Chentao and Guo, Song and Ding, Yue and Li, Jie, ``Adaptive incentivize for cross-silo federated learning in IIoT: A multi-agent reinforcement learning approach,'' \textit{IEEE Internet Things J.}, 2023.\\[6pt]
			\cite{zhang2023multi} Zhang, Jing and Shen, Fei and Tang, Liang and Yan, Feng and Qin, Fei and Wang, Chao, ``A Multi-Agent Reinforcement Learning Approach for Dynamic Offloading with Partial Information-Sharing in IoT Networks,'' \textit{2023 IEEE 98th Vehicular Technology Conference (VTC2023-Fall)}, pp. 1--5, 2023.\\[6pt]
			\cite{tang2022uav} Tang, Qiang and Liu, Lixin and Jin, Caiyan and Wang, Jin and Liao, Zhuofan and Luo, Yuansheng, ``An UAV-assisted mobile edge computing offloading strategy for minimizing energy consumption,'' \textit{Computer Networks}, vol. 207, pp. 108857, 2022.\\[6pt]
			\cite{seo2022differential} Seo, Hyeonseok and Oh, Hyeontaek and Choi, Jun Kyun and Park, Sangdon, ``Differential pricing-based task offloading for delay-sensitive IoT applications in mobile edge computing system,'' \textit{IEEE Internet Things J.}, vol. 9, no. 19, pp. 19116--19131, 2022.\\[6pt]
			\cite{guo2022energy} Guo, Mian and Li, Qirui and Peng, Zhiping and Liu, Xiushan and Cui, Delong, ``Energy harvesting computation offloading game towards minimizing delay for mobile edge computing,'' \textit{Computer Networks}, vol. 204, pp. 108678, 2022.\\[6pt]
			\cite{li2022joint} Li, Yuwei and Yang, Bo and Wu, Hao and Han, Qiaoni and Chen, Cailian and Guan, Xinping, ``Joint offloading decision and resource allocation for vehicular fog-edge computing networks: A contract-stackelberg approach,'' \textit{IEEE Internet Things J.}, vol. 9, no. 17, pp. 15969--15982, 2022.\\[10pt]}\\}
\end{my}

(c)

@@

\newpage

\section{Response to Reviewer 2}
\begin{enumerate}

	\item \underline{Reviewer's Comment}: 
	\textit{``The authors should provide a comparative table to highlight their contributions. Specially, the authors should compare their method with other references on computation task offloading cited in the paper, including aspects such as scenarios, methods, advances, drawbacks, and so on.''} \newline

	\underline{Authors' Reply}: To address the reviewer's comment, we have included a table in the 'Related Works' subsection that compares the key characteristics of relevant studies, as below:
	\begin{table*}[htbp]\textcolor{blue}{
			\renewcommand{\arraystretch}{0.6}
			\captionsetup{name=TABLE}
			\caption{\textcolor{blue}{Comparison of Related Works Characteristic\vspace{4mm}}}
			\scalebox{0.7}{%
				\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3cm}p{4.6cm}l} 
					\toprule
					\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
					\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a singel MEC system model  \\\midrule
					\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule				
					\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
					\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent DDPG & Not take user's deman into consideration \\\midrule
					\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
					\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
